A Simplified Spectral Deferred Correction Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2020-09-26 simplified_sdc_intro/paper.tex
update
more notes
updates

For Strang split coupling of hydro and reactions, $DX_k/Dt = 0$,
and our evolution equations are:
\begin{align}
\frac{DY_e}{Dt} &= \sum_k \frac{Z_k}{A_k} \frac{DX_k}{Dt} = 0 \\
\frac{D}{Dt} \frac{1}{\bar{A}} &= - \frac{1}{\bar{A}^2} \frac{D\bar{A}}{Dt} = \sum_k \frac{1}{A_k} \frac{DX_k}{Dt} = 0 \rightarrow \frac{D\bar{A}}{Dt} = 0 \\
\frac{D}{Dt} \left (\frac{B}{A} \right ) &= \sum_k \frac{B_k}{A_k} \frac{DX_k}{Dt} = 0
\end{align}
Therefore each of these auxillar equations obeys an advection
equation in the hydro part of the advancement.  In the SDC algorithm,
there will be a reactive source (an $\Ic_q$) for each of these that is
computed in the same manner as above.

@@

  In addition to initializing the mass fractions, $X_k$, we also fill
  the auxiliary composition data, $Y_e$, $\bar{A}$, and $(B/A)$, using
  these $X_k$.

@@

@@

>>>>

and our evolution equations are:
\begin{align}
\frac{DY_e}{Dt} &= \sum_k \frac{Z_k}{A_k} \frac{DX_k}{Dt} = \sum_k \frac{Z_k}{A_k} \omegadot_k \\
\frac{D\bar{A}}{Dt} &= -\bar{A}^2 \sum_k \frac{1}{A_k} \frac{DX_k}{Dt} = -\bar{A}^2 \sum_k \frac{1}{A_k} \omegadot_k \\
\frac{D}{Dt} \left (\frac{B}{A} \right ) &= \sum_k \frac{B_k}{A_k} \frac{DX_k}{Dt} = \sum_k \frac{B_k}{A_k} \omegadot_k
\end{align}
For Strang split coupling of hydro and reactions, $DX_k/Dt = 0$,
Therefore each of these auxillary equations obeys an advection
equation in the hydro part of the advancement.  In the SDC algorithm,
there will be a reactive source (an $\Ic_q$) for each of these that is
computed in the same manner as above.

@@

  We initializing the mass fractions, $X_k$, and then compute the
  electron fraction, $Y_e$, from them.  For the two other composition
  quantities we carry, $\bar{A}$, and $(B/A)$, we need values that are
  consistent with the value of $Y_e$ and the nuclei stored in the NSE
  table.  Therefore, if the thermodynamic conditions put us in NSE
  (using the conditions defined below), then we get $\bar{A}$ and
  $(B/A)$ from the NSE table.  Otherwise, we compute these directly
  from $X_k$.  $X_k$.

@@

Also explore: PLM vs PPM, 1 vs. 2 vs. 3 iterations

\subsection{NSE convergence test problem}

To test the coupling of the NSE table to the hydrodynamics, we run a
similar problem as above, except with the thermodynamic conditions
appropriate for the matter to be in NSE.

@@

Look at number of SDC iterations too.

How does the timestep limiter work in the middle of SDC iterating?

aprox21

look at number of RHS calls, wallclock time

output every step and then for a single zone plot enuc every timestep to see if it oscillates
